Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-14 paper/paper.tex
Smooth SU2 section

This package is a preCICE adapter~\cite{Uekermann2017_Adapters} for the CFD code SU2 and extends the original SU2 source code by patching the files.
For this, the adapter provides a custom script that needs to be executed before the build phase.
Nix offers the patchPhase that allows us to run the script in this phase and patch the original source, after that the \texttt{stdenv} automatically recognizes that the repository uses autotools for building the software and runs the configurePhase.

We additionally needed to add the two configureFlags \texttt{--with-include} and \texttt{--with-lib} to the preCICE install directory because otherwise autoconf does not find the preCICE installation directory.

>>>>

The SU2-preCICE adapter~\cite{Uekermann2017_Adapters} patches and extends the original CFD code SU2 \todo{cite SU2}.
To this end, the adapter provides a script to run before the build phase.
We do this in Nix' patch phase. Afterwards, \texttt{stdenv} automatically recognizes that SU2 uses autotools for building and runs the configure phase.
Finally, to find the preCICE installation, we need to set the configuration flags \texttt{--with-include} and \texttt{--with-lib}.
